### 2015-10-03 untitled.tex
edited untitled.tex

In this report, we make two observations pertaining to this question:
\begin{enumerate}
	\item There exist sporadic segmented self-suspending task sets that are schedulable under fixed-priority scheduling without any enforcement, but the corresponding schedule by using the period enforcer algorithm is not feasible. This shows that Theorem 5 in \cite{Raj:suspension1991} has to be  used with care --- it may be applied only in the context of the transformed single-segment deferrable task set, and not in the context of the original segmented self-suspending task set.

@@

\section{Schedulable Self-Suspending Tasks but Unschedulable Period Enforcer}
\label{sec:unschedulable}

Let's consider a task system with $2$ tasks. Let $C_1 = 2$ and $T_1=D_1=10$ (without self-suspension). Let $C_{2,1} = 1, S_{2,1} = 6, C_{2,2}=1, T_2=D_2=11$. Suppose that we use the rate-monotonic priority assignment, i.e., $\tau_1$ has higher priority than $\tau_2$. This task system is feasible without any enforcement since at most one computation segment of a job of $\tau_2$ can be affected by $\tau_1$. The worst-case response time of task $\tau_2$ is hence $10$.

>>>>

In this report, we make two observations pertinent to this question:
\begin{enumerate}
	\item There exist sporadic segmented self-suspending task sets that are schedulable under fixed-priority scheduling without any enforcement, but the corresponding schedule by using the period enforcer algorithm is not feasible. This shows that Theorem 5 in \cite{Raj:suspension1991} has to be  used with care --- it may be applied only in the context of the transformed single-segment deferrable task set, and not in the context of the original segmented self-suspending task set.

@@

\section{Deadline Missses Caused by Period Enforcement}
\label{sec:unschedulable}

In this section, we demonstrate with an example that there exist sets of segmented self-suspending sporadic tasks that both \textbf{(i)} are schedulable \emph{without} period enforcement and \textbf{(ii)} are not schedulable under the period enforcer.

Consider a task system with $2$ tasks. Let $C_1 = 2$ and $T_1=D_1=10$ (without self-suspension). Let $C_{2,1} = 1, S_{2,1} = 6, C_{2,2}=1, T_2=D_2=11$. Suppose that we use the rate-monotonic priority assignment, i.e., $\tau_1$ has higher priority than $\tau_2$. This task system is feasible without any enforcement since at most one computation segment of a job of $\tau_2$ can be affected by $\tau_1$. The worst-case response time of task $\tau_2$ is hence $10$.
